---
title: "Recitation1"
output:
  pdf_document: 
    keep_tex:  true
  html_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## Marathon Dataset

The *summary* function provides min, max, mean, median, 1st quantile and 3rd quantile information for each column in the dataframe. 

```{r}
marathon <- read.csv('marathon.csv');
summary(marathon)
```

We see that the Marathon dataset contains 2 columns (Year and Time). When the dataset is large, we usually skim the dataset by examing the first few rows. This can be achieved with the function *head*, where the second input indicates the number of rows to be displayed. Similarly, *tail* function is used to examine the last few rows. 

```{r}
head(marathon,10)
```

To access a particular column, say the Time column, we can use the command *marathon$Time* or *marathon["Time"]*. The former outputs a vector, and the latter outputs another dataframe. 

Compare 

```{r}
marathon$Time
```

with

```{r}
marathon['Time']
```

Finally, let us plot Time versus Year of the Marathon dataset. We can have either scatter plot

```{r}
plot(marathon$Year, marathon$Time)
```

or the time series plot:

```{r}
ts.plot(marathon$Time)
```


## Sleep Dataset

The Sleep dataset is a built-in dataset in R. Let us first gather some information about this dataset. 

```{r}
attributes(sleep)
```
It has three columns, extra, group and ID. 

Boxplot is a nice way to visualize the data, let us try for the extra column: the increase in the number of hours of sleep resulting from either drug.

```{r}
boxplot(sleep['extra'])
```

In some data analysis, we need to focus on a subset of the data. For instance, we want to separate group=1 and group=2. This can be achieved using the following command:

```{r}
group1 <- subset(sleep,group==1);
group2 <- subset(sleep,group==2)
```

We can check group1 and group 2:

```{r}
group1
```

```{r}
group2
```

Now we can do a side by side comparison for the extra column between two groups in order to understand the effects of these two types of drugs. 

```{r}
boxplot(group1$extra,group2$extra)
```

