\documentclass{article}    % Specifies the document style.
\renewcommand{\baselinestretch}{1}      % Spacing
\setlength{\oddsidemargin}{0in} \setlength{\evensidemargin}{0in} \setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-.2in} \setlength{\headsep}{0in} \setlength{\textheight}{9.5in}
\pagestyle{empty}
%
\usepackage{color}
\usepackage{placeins}
\usepackage{amsmath,amsthm}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{url}


\begin{document}           % End of preamble and beginning of text.
	\begin{center}
		
		\textbf{\large{ENGRD 2700: Basic Engineering Probability and
				Statistics\medskip \\ Fall 2019}}\bigskip
		
		\vskip 0.25em
		
		\textbf{\large{Homework 7}} 
	\end{center}
	
	\vskip 1em
	
	\noindent Due \textbf{Friday Nov 22} at 11:59 pm. Submit to Gradescope by clicking the name of the assignment. See \url{https://people.orie.cornell.edu/yudong.chen/engrd2700_2019fa.html#homework} for detailed submission instructions. 
	
	\vskip 1em
	
	
	The same stipulations from Homework 1 (e.g., independent work, computer code, etc.) still apply. \bigskip
	
	\vskip 1em
	
	
	\begin{enumerate}
		\item A sample of 100 service times at a call center has a sample mean of 9 minutes and a sample standard deviation of 6 minutes. Assume that the service times are independent and have a normal distribution.
		\begin{enumerate}
			\item Give a 95\% confidence interval for the mean service time.
			
			\item Approximately how many service times we would have to collect
			to return a 95\% confidence interval whose width is at most 15 seconds (= 1/4 minutes)?
		\end{enumerate}

		\item Harry owns a bakery. The number of chocolate chips that he adds to his cookies is normally distributed with mean $\mu$ and variance $\sigma^2 = 25$, where $\mu$ is unknown. 
		A customer buys a dozen of these cookies, and obtains the simple random sample
		$$
		31, \, 23, \, 42, \, 44, \, 28, \, 34, \, 19, \, 29, \, 30, \, 25, \, 28, \, 27
		$$
		\begin{enumerate}
			\item Compute a 95\% confidence interval for $\mu$. 

			\item  Compute 90\% and 99\% confidence intervals for $\mu$.
			
			\item  Suppose the customer wants a 95\% confidence interval that has a width of at most 2. How many cookies would he need to buy to achieve this?
		\end{enumerate}
		
		\item Alice and Bob are running for state governor, and two polling agencies, Company X and Company Y, decide to gauge public opinion.
		\begin{enumerate}
			\item Company X interviews $453$ people, and finds that $55\%$ of individuals want to vote for Alice. Construct a $95\%$ confidence interval for $p$, the proportion of all voters in the state supporting Alice. 

			\item  Company Y conducts its own independent study, and obtains the interval $[0.492,0.568]$ from a sample size of $378$. What confidence level did Company Y use?

			\item Suppose, contrary to the information specified in part (b), that Company Y obtained the $90\%$ confidence interval $[0.509,0.591]$ instead. How many individuals did Company Y interview?
		\end{enumerate}

		\item The files \texttt{ithaca.csv} and \texttt{syracuse.csv} contain daily temperature data in Ithaca and Syracuse during the month of March. Import these datasets into R or RStudio.
		\begin{enumerate}
			\item  Let $\mu_i$ and $\mu_s$ denote the mean temperatures in both cities during the month of March. Construct a $97\%$ confidence interval for $\mu_i-\mu_s$. 

			\item  Repeat part (a), assuming the temperature in Ithaca is independent of the temperature in Syracuse (which is not true in reality). How do your intervals compare?
		\end{enumerate}
		
		\item Luigi is known far and wide for his meatball subs. Although he advertises that the subs weigh 400 g, Vinny, a regular, suspects that the subs weigh less. Vinny buys a sub each day for 81 consecutive days. He obtains the 95\% confidence interval $[393.08, \, 400.92]$ for the mean weight $\mu$ of a sub.
		\begin{enumerate}
			\item Find $\bar x$ and $s$, the mean and standard deviation of his sample.

			\item  Approximately how many subs would Vinny need to buy in order to halve the width of his confidence interval?
			
			\item Compute 90\% and 99\% confidence intervals for $\mu$.
		\end{enumerate}
	\end{enumerate}
	
\end{document}

